### 2021-04-23 ms/suppmat.tex
Edits resulting from comments to reviewers ICES JMS

\noindent
Sebasti\'{a}n A. Pardo\textsuperscript{1*}, Geir H. Bolstad\textsuperscript{2}, J. Brian Dempson\textsuperscript{3}, 
        Julien April\textsuperscript{4}, Ross A. Jones\textsuperscript{5}, %Martha J. Robertson\textsuperscript{3}, 
        Dustin Raab\textsuperscript{6}, Jeffrey A. Hutchings\textsuperscript{1}
\newline

\noindent
\small{\textsuperscript{1} Department of Biology, Dalhousie University, Halifax, NS, Canada\\}
\small{\textsuperscript{2} Norwegian Institute for Nature Research (NINA), Trondheim, Norway\\}
\small{\textsuperscript{3} Fisheries and Oceans Canada, St. John's, NL, Canada\\}
\small{\textsuperscript{4} Minist\`{e}re des For\^{e}ts, de la Faune et des Parcs, Qu\'{e}bec, QC, Canada\\}
\small{\textsuperscript{5} Fisheries and Oceans Canada, Moncton, NB, Canada\\}
\small{\textsuperscript{6} Fisheries and Oceans Canada, Dartmouth, NS, Canada\\}
\small{\textsuperscript{*} Corresponding author: spardo@dal.ca}
\beginsupplement

@@

where $P(N_{obs,r,t,s,a}|n_{r,t,s,a})$ is the probability of having a specific number of returns $N_{r,t,s,a}$ given 
$n_{r,t,s,a}$, which is the number of scale samples in river r, year t, of returning age a, and of size group s;
$N_{r,t,s}$ is the total number of returns in river r, year t, and of size group s;
$N_{r,t,s} - N_{r,t,s,a}$ is the total numbers of returns in river r, year t, of size group s that are \textbf{not} of returning age a;
and $n_{r,t,s}$ is the total number of scale samples in river r, year t, and of size group s.
We iterated through all possible values of $N_{r,t,s,a}$ (i.e. from zero to $N_{r,t,s}$), to obtain a probavility for each value, which
we then used as weighting probabilities to sample 10,000 random draws of $N_{r,t,s,a}$, which we denote as $\hat{N}_{r,t,s,a}$. 
We then add the draws of the same age from both size groups to obtain a vector of estimates of number of returns of a given age a (i.e. 1SW or 2SW) for a given river and year ($\hat{N}_{r,t,a}$):

@@

There are a number of years with very few scales samples, particularly for the
Campbellton population, and one year for this population (2011) with no scales
samples. Under these conditions, the model provides high estimates of
$\epsilon$, but which are somewhat constrained by the log-transformation of
abundance draws of a uniform distribution. Thus, the value of $\epsilon$ for
2011, the year with no scale samples, is of 0.711 (Table~\ref{tab:epsilon1}),
which is likely an underestimate of true uncertainty given the absence of
data. Nonetheless, the model results in small $\epsilon$ values for years
where there are ten or more scale samples. 
For years where there are no scale nor return samples to draw inferences from (e.g. a year for which there are no small 2SW scales, nor large scale samples),
sometimes the error for 2SW returns cannot be estimated; in these cases we set the value of $\epsilon_{2}$ to 0.999.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/camp-scale-epsilon-example.png} \caption{Example
        of the estimation of $\epsilon_{1}$ for two different years of data for the Campbellton population: year 2011 where
        there were no scale samples, and year 2014 with a large number of scales samples. a) Distribution of draws of potential
    1SW abundances, adding the estimates from both small and large returns, for the year 2011. Note that the distribution spans the whole range of
returns (up to 5443). b) The same distribution but log-transformed, which results in a right-skewed distribution. The blue line represents the normal
distribution fitted to the log-transformed data, from which $\epsilon_{1}$ is equal to its standard deviation. b) Distribution of draws of potential
    1SW abundances, adding the estimates from both small and large returns, for the year 2014, which is much tightly constrained. d) The distribution
of log-transformed abundance draws for year 2014. In this case, the normal distribution fitted is much tighter and more closely resembles the underlying histogram,
and results in a much lower estimate of $\epsilon_{1}$.}
    \label{fig:priors} 
\end{figure}

@@

\subsection*{Error in smolt abundances used in the model}

>>>>

\noindent
Sebasti\'{a}n A. Pardo\textsuperscript{1*}, Geir H. Bolstad\textsuperscript{2}, J. Brian Dempson\textsuperscript{3},
        Julien April\textsuperscript{4}, Ross A. Jones\textsuperscript{5}, %Martha J. Robertson\textsuperscript{3},
        Dustin Raab\textsuperscript{6}, Jeffrey A. Hutchings\textsuperscript{1,7,8}
\newline

\noindent
\small{\textsuperscript{1} Department of Biology, Dalhousie University, Halifax, NS, Canada\\}
\small{\textsuperscript{2} Norwegian Institute for Nature Research (NINA), Trondheim, Norway\\}
\small{\textsuperscript{3} Fisheries and Oceans Canada, St. John's, NL, Canada\\}
\small{\textsuperscript{4} Minist\`{e}re des For\^{e}ts, de la Faune et des Parcs, Qu\'{e}bec, QC, Canada\\}
\small{\textsuperscript{5} Fisheries and Oceans Canada, Moncton, NB, Canada\\}
\small{\textsuperscript{6} Fisheries and Oceans Canada, Dartmouth, NS, Canada\\}
\small{\textsuperscript{7} Institute of Marine Research, Flødevigen Marine Research Station, N-4817 His, Norway\\}
\small{\textsuperscript{8} Centre for Coastal Research, University of Agder, N-4604 Kristiansand, Norway\\}
\small{\textsuperscript{*} Corresponding author: spardo@dal.ca}
\beginsupplement

@@

where $P(N_{obs,r,t,s,a}|n_{r,t,s,a})$ is the probability of having a specific number of returns $N_{r,t,s,a}$ given
$n_{r,t,s,a}$, which is the number of scale samples in river r, year t, of returning age a, and of size group s;
$N_{r,t,s}$ is the total number of returns in river r, year t, and of size group s;
$N_{r,t,s} - N_{r,t,s,a}$ is the total numbers of returns in river r, year t, of size group s that are \textbf{not} of returning age a;
and $n_{r,t,s}$ is the total number of scale samples in river r, year t, and of size group s.
We iterated through all possible values of $N_{r,t,s,a}$ (i.e. from zero to $N_{r,t,s}$), to obtain a probability for each value, which
we then used as weighting probabilities to sample 10,000 random draws of $N_{r,t,s,a}$, which we denote as $\hat{N}_{r,t,s,a}$.
We then add the draws of the same age from both size groups to obtain a vector of estimates of number of returns of a given age a (i.e. 1SW or 2SW) for a given river and year ($\hat{N}_{r,t,a}$):

@@

There are a number of years with very few scales samples, particularly for the
Campbellton population, and one year for this population (2011) with no scales
samples. Under these conditions, the model provides high estimates of
$\epsilon$, but which are somewhat constrained by the log-transformation of
abundance draws of a uniform distribution. Thus, the value of $\epsilon$ for
2011, the year with no scale samples, is of 0.719 (Table~\ref{tab:epsilon1}),
which is likely an underestimate of true uncertainty given the absence of
data. Nonetheless, the model results in small $\epsilon$ values for years
where there are ten or more scale samples.
For years where there are no scale nor return samples to draw inferences from (e.g. a year for which there are no small 2SW scales, nor large scale samples),
sometimes the error for 2SW returns cannot be estimated; in these cases we set the value of $\epsilon_{2}$ to 0.999.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/camp-scale-epsilon-example.png} \caption{Example
        of the estimation of $\epsilon_{1}$ for two different years of data for the Campbellton population: year 2011 where
        there were no scale samples, and year 2014 with a large number of scales samples. a) Distribution of draws of potential
    1SW abundances, adding the estimates from both small and large returns, for the year 2011. Note that the distribution spans the whole range of
returns (up to 5443). b) The same distribution but log-transformed, which results in a right-skewed distribution. The blue line represents the normal
distribution fitted to the log-transformed data, from which $\epsilon_{1}$ is equal to its standard deviation. c) Distribution of draws of potential
    1SW abundances, adding the estimates from both small and large returns, for the year 2014, which is much more tightly constrained. d) The distribution
of log-transformed abundance draws for year 2014. In this case, the normal distribution fitted is much tighter and more closely resembles the underlying histogram,
and results in a much lower estimate of $\epsilon_{1}$.}
    \label{fig:priors}
\end{figure}

@@

\subsection*{Uncertainty in smolt abundances used in the model}
